Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-21 snapshot_system/fast14_deduplication.tex
paper revisions
revised evaluation
revised evaluation etc

\subsection{Storage Space and Impact on Fault Tolerance}

@@

The replication degree of the backup storage 
is $r$ for regular file blocks and $r=3$ is a typical setting in distributed
file systems~\cite{googlefs03,hdfs10}.
In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 
The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
$ k*r_c  + (c_u-k)*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
\[
\sigma \frac{r_c}{r} + 1-\sigma
\]
Since $\sigma$ is small (it is 2\% in our experiments),  
term $\sigma \frac{r_c}{r}$ is small in the above expression.  
Thus the impact on storage increase is very small even when we choose a large $\frac{r_c}{r}$ ratio. 
For example, $\frac{r_c}{r}=2$ or 3.

@@

Thus $N_1$ is much smaller than $N_o$. 
When there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a much lower chance to lose a snapshot than VO. 
Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
our test dataset.
%which shows how many VMs the failure of a single block can affect. 
For VC, we only show
the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
one VM.
Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
%From data, 
%we have observed that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
%This is likely because the PDS FSBs tightly pack data used by many VMs, 
%which decreases the overall number of FSBs required to backup a VM.
Noted that  if  the backup for multiple VMs were conducted concurrently, there would be more
VMs shared  by each file block on average in VO. 
%Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. VMs sharing FSB},
                cycle list name=mline,
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured average number of VMs sharing a 64MB FSB in VO and in VC.}
  \label{fig:fsb-links}
\end{figure}

@@

\item
When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
\begin{equation}
\label{eq:VC2}
% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
% *
% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
A(r)^{N_1} * A(r_c)^{N_2}
\end{equation}
Figure~\ref{fig:fsb-availability} illustrates the $A(r)$ values with
%that the availability of an individual file system block
with different replication degrees. This demonstrates inequality 
% $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
$A(r) < A(r_c)$.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
these two conditions support that VC has a  higher availability. 
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize}

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={Availability of Single FSB (\%)},
            %extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of a file system block in a 100 machine cluster with different replication 
and failure settings.THIS PLOT WILL BE REPLACED BY TABLE}
  \label{fig:fsb-availability}
\end{figure}

>>>>

\subsection{Storage Space and Impact on Fault Isolation}

@@

The replication degree of the backup storage 
is $r$ for regular file blocks and $r=3$ is a typical setting in distributed
file systems~\cite{googlefs03,hdfs10}.
In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 
The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
$ k*r_c  + (c_u-k)*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
\[
\sigma \frac{r_c}{r} + 1-\sigma.
\]
Since $\sigma$ is small (it is 2\% in our experiments),  
term $\sigma \frac{r_c}{r}$ is small in the above expression.  
Thus the impact on storage increase is very small even when we choose a large $\frac{r_c}{r}$ ratio. 
For example, $\frac{r_c}{r}=2$ or 3.

@@

Thus $N_1$ is much smaller than $N_o$. 
When there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a much lower chance to lose a snapshot than VO. 
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
%our test dataset.
%For VC, we only show
%the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
%one VM.
%Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from our test data.
Figure~\ref{fig:vm-links} shows the average number of file system blocks for each VM in VC and in VO. 
From data, we have observed that $N_1 +N_2 < N_o$ in practice. 
This is likely because the PDS FSBs tightly pack data used by many VMs, 
which decreases the overall number of FSBs required to backup a VM.
Noted that  if  the backup for multiple VMs were conducted concurrently, there would be more
VMs shared  by each file block on average in VO.

%Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.

\comments{
\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. VMs sharing FSB},
                cycle list name=mline,
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured average number of VMs sharing a 64MB FSB in VO and in VC.}
  \label{fig:fsb-links}
\end{figure}

}

@@

\item
When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
\begin{equation}
\label{eq:VC2}
% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
% *
% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
A(r)^{N_1} * A(r_c)^{N_2}
\end{equation}
Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
%that the availability of an individual file system block
with different replication degrees. This demonstrates inequality 
% $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
$A(r) < A(r_c)$.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
these two conditions support that VC has a  higher availability. 
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize}

\comments{
\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={Availability of Single FSB (\%)},
            %extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of a file system block in a 100 machine cluster with different replication 
and failure settings.THIS PLOT WILL BE REPLACED BY TABLE}
  \label{fig:fsb-availability}
\end{figure}
}

\begin{table}
    \footnotesize
    \tabcolsep=0.11cm
    \begin{tabular}{|l|l|l|l|}
        \hline
        \multirow{2}{*}{Failures}   & \multicolumn{3}{c|}{FSB Availability} \\
                                    %\cline{2-4}
                                    & $R_c=3$ & $R_c=6$ & $R_c=9$ \\
        \hline
        3 & 99.999 & 100 & 100\\
        5 & 99.994 & 100 & 100\\
        10 & 99.925 & 99.999 & 99.999\\
        20 & 99.295 & 99.997 & 99.999 \\
        \hline
    \end{tabular}
    \caption{Availability of individual 64MB Filesystem blocks (FSBs) as storage
    nodes fail in a 100 node cluster.}
    \label{tab:fsb-availability}
\end{table}

### 2013-09-21 snapshot_system/fast14_evaluation.tex
figure changes
revised evaluation etc

\subsection{Impact on Fault Tolerance}

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 25 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
We show three snapshot  availability curves as the number of machines failed increases.
%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
Curve ``VC(worst-case)" represents the situation that each PDS file system block is shared by all VMs.
%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
%count the number of dependencies from a file system block to VM.
%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
%Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
%For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
%while VC with 99.9\% loses snapshots of 2.5 VMs.
%The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
%and packs  data blocks for one VM as much as possible.  The extra replication
%for PDS blocks also significantly increases the snapshot availability even when
%a PDS file block is shared by every VM.
%=======
%Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
%as storage nodes fail. 
%We assume a random distirbution of 64MB filesystem
%blocks (FSBs). where FSBs are not randomly distributed availability might
%be improved by limiting the number of storage nodes a particualr VM depends
%on but we take the conservative approach. We compare VO, the expected case for
%VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
%based on measured values in our dataset.
To obtain VM sharing of file blocs, we perform perfect deduplication over 105 VMs, 
append unique chunks to a DFS file and
count the number of dependencies from a file system block to VM.
%In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
Our results show that even the worst case for VC has a higher availability than VO.
%Our VM-centric approach shows significant improvements
%in VM availability.
For example, with 5/100 machines failed, VO with 93.3\% availability would lose data in 169 VMs 
while VC with 99.9\% loses data for 2 VMs.
The key reason is that for most data in VC, only a single
VM can be affected by the loss of a single FSB.
% because our VM-centric approach
%localizes deduplication.

@@

\end{figure}
}
\begin{table}
    \footnotesize
    \tabcolsep=0.11cm
    \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        \multirow{3}{*}{Failures}   & \multicolumn{6}{c|}{Snapshot Availability} \\
                                    %\cline{2-7}
                                    & \multicolumn{3}{c|}{$p=100$} & \multicolumn{3}{c|}{$p=1000$} \\
                                    %\cline{2-7}
                                    & VO & VC & VC(WC) & VO & VC & VC(WC) \\
        \hline
        3 & 99.304 & 99.891 & 99.891 & 99.999 & 99.999 & 99.999\\
        5 & 93.256 & 98.919 & 98.919 & 99.993 & 99.999 & 99.999\\
        10 & 43.251 & 87.707 & 87.638 & 99.919 & 99.987 & 99.987\\
        20 & 0.034 & 24.953 & 21.571 & 99.228 & 99.879 & 99.879\\
        \hline
    \end{tabular}
    \caption{Availability of VM snapshots for VO and VC. VC(WC) stands for the case that a 
PDS file block is shared by all VMs.}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=10,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{$R_C=4$,$R_C=5$,$R_C=6$, $R_C=9$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
  \label{fig:pds-replication}
\end{figure}

@@

{\bf Storage cost of replication.} 
%Table ~\ref{tab:replication_cost} shows the total storage space required by 
%VC as the PDS replication degree changes while non-PDS replication degree is fixed as 3. 
The total storage  for all VM snapshots in each physical machine takes about 3.065TB on aveage when
the replication degree of both PDS and non-PDS data is 3. 
Allocating  one extra  copy for PDS data only adds  7GB in total per machine.
Thus PDS replication degree 6 only adds the total space by 0.685\% while PDS replication degree 9 adds 1.37\% 
space overhead, which is still small.
%The increase in storage cost is minimal because the PDS makes up a 
%small percent of the total storage space, while increasing replication degree has a  more significant benefit for
%availability as shown in Figure~\ref{fig:pds-replication}.

@@

{\bf Memory and disk bandwidth usage with multi-VM processing}. 
We have further studied the memory and disk bandwidth usage 
when running concurrent VM snapshot backup on each machine with $\delta=2\%$. 
Table ~\ref{tab:resource_usage} gives the CPU, memory and disk read/write  workload when
running 1 or multiple  backing tasks at the same time on each physical machine. 
Disk read is controled as 50MB/s bandwidth usage so that other cloud services are not impacted a lot.
% [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
% the cloud infrastructure services and are shared among many applications.]
The memory usage includes 100MB of PDS index and other space cost for executing deduplication tasks such as 
receipt metadata and cache. 
%We see our hybrid deduplication scheme only occupies a small amount of system resources. 
%The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
%memory during duplicate detection.

Table ~\ref{tab:resource_usage} shows that  a single backup task per node can complete the backup of the entire
VM cluster in about 1.58 hours. Since there are about 25 VMs per machine, we could execute
more tasks in parallel at each machine. But adding more bakcup concurrency does not shorten the overall time
a lot because of the controlled  disk read time.
%,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
%at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.

{\bf Processing Time breakdown}.
Figure~\ref{fig:vc_srb_combined} shows
the  average  processing  time of  a VM segment under VC and SRB. 
It has a breakdown of time for reading data, updating the metadata, network latency to visit
a remote machine, and index access for fingerprint comparison.
SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
it relies on this local machine to access its index (often on the disk, supported by a Bloom filter) 
and perform comparison.
VC is faster for index access because it conducts in-memory local search first and then
accesses  the PDS on distributed shared memory.  
SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
local meta data index.
Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.

@@

Figure~\ref{fig:vc_srb_combined} also reports the average backup time for a VM in VC when
varying the PDS size.  It lists the time distribution for data reading,
similarity-guided local search, cross-VM PDS lookup, and non-duplicate data writing. 
While data reading dominates the backup process, PDS lookup spends about a similar amount
of time as local search.
The change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time.

@@

\begin{table*}[t]
    \centering
    \begin{tabular}{c|ccc|ccc}
    Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
    backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
    per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
    1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
    2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
    4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
    6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
    \end{tabular}
\caption{Backup throughput under different concurrency}
\label{tab:throughput}
\end{table*}
{\bf Throughput.}
Table~\ref{tab:throughput} shows the  backup throughput per each machine when all machine nodes 
handle  several VMs in parallel.
To begin, on each node we write snapshots for 4 VMs concurrently, and gradually 
increase number of VMs to 12 to saturate our system capability. We observed 
the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
which is far beyond our QFS file system capability. The reason behind it is our efficient
deduplication architecture and compression which greatly reduce the amount of data that needs to be written to
the file system. The main bottleneck here is that our QFS installation only
manages one disk per node, which prevents it from fully utilizing the the
benefits of parallel disk access. We expect our architecture can
perform even better in production clusters, which often have ten or more disks on each node.

@@

% \subsection{Effectiveness of Approximate Deletion}
% \begin{figure}
%     \centering
%     \includegraphics[width=3in]{figures/leakage}
%     \caption{Accumulated storage leakage by approximate snapshot deletions}
%     \label{fig:leakage}
% \end{figure}

>>>>

\subsection{Impact on Fault Isolation}

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 25 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
We show three snapshot  availability curves as the number of machines failed increases.
%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
Curve ``VC(WC)" represents a worst-case  situation that each PDS file system block is shared by all VMs.
%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
%count the number of dependencies from a file system block to VM.
%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
%Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
%For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
%while VC with 99.9\% loses snapshots of 2.5 VMs.
%The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
%and packs  data blocks for one VM as much as possible.  The extra replication
%for PDS blocks also significantly increases the snapshot availability even when
%a PDS file block is shared by every VM.
%=======
%Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
%as storage nodes fail. 
%We assume a random distirbution of 64MB filesystem
%blocks (FSBs). where FSBs are not randomly distributed availability might
%be improved by limiting the number of storage nodes a particualr VM depends
%on but we take the conservative approach. We compare VO, the expected case for
%VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
%based on measured values in our dataset.
To obtain VM sharing of file blocs, we perform perfect deduplication over 105 VMs, 
append unique chunks to a DFS file and
count the number of dependencies from a file system block to VM.
%In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
Our results show that even the worst case for VC has a higher availability than VO.
%Our VM-centric approach shows significant improvements
%in VM availability.
For example, with 5/100 machines failed, VO with 93.3\% availability would lose data in 169 VMs 
while VC with 99.9\% loses data for 2 VMs.
The key reason is that for most data in VC, only a single
VM can be affected by the loss of a single FSB.
% because our VM-centric approach
%localizes deduplication.

@@

\end{figure}
}
\begin{table}
    \footnotesize
    \tabcolsep=0.11cm
    \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        \multirow{3}{*}{Failures}   & \multicolumn{6}{c|}{Snapshot Availability} \\
                                    %\cline{2-7}
                                    & \multicolumn{3}{c|}{$p=100$} & \multicolumn{3}{c|}{$p=1000$} \\
                                    %\cline{2-7}
                                    & VO & VC & VC(WC) & VO & VC & VC(WC) \\
        \hline
        3 & 99.304 & 99.891 & 99.891 & 99.999 & 99.999 & 99.999\\
        5 & 93.256 & 98.919 & 98.919 & 99.993 & 99.999 & 99.999\\
        10 & 43.251 & 87.707 & 87.638 & 99.919 & 99.987 & 99.987\\
        20 & 0.034 & 24.953 & 21.571 & 99.228 & 99.879 & 99.879\\
        \hline
    \end{tabular}
    \caption{Availability of VM snapshots for VO and VC.}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=20,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{$R_C=4$,$R_C=5$,$R_C=6$, $R_C=9$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
  \label{fig:pds-replication}
\end{figure}

@@

{\bf Storage cost of replication.} 
%Table ~\ref{tab:replication_cost} shows the total storage space required by 
%VC as the PDS replication degree changes while non-PDS replication degree is fixed as 3. 
The total storage  for all VM snapshots in each physical machine takes about 3.065TB on average when
the replication degree of both PDS and non-PDS data is 3. 
Allocating  one extra  copy for PDS data only adds  7GB in total per machine.
Thus PDS replication degree 6 only adds the total space by 0.685\% while PDS replication degree 9 adds 1.37\% 
space overhead, which is still small.
%The increase in storage cost is minimal because the PDS makes up a 
%small percent of the total storage space, while increasing replication degree has a  more significant benefit for
%availability as shown in Figure~\ref{fig:pds-replication}.

@@

{\bf Memory and disk bandwidth usage with multi-VM processing}. 
We have further studied the memory and disk bandwidth usage 
when running concurrent VM snapshot backup on each machine with $\delta=2\%$. 
Table ~\ref{tab:resource_usage} gives the resource usage  when
running 1 or multiple  VM backup tasks at the same time on each physical machine. 
CPU column is the percentage of a core usage. 
The memory usage includes 100MB of PDS index and other space cost for executing deduplication tasks such as 
receipt metadata and cache. 
Disk read is controlled as 50MB/s bandwidth usage so that other cloud services are not impacted a lot.
Disk write is the write usage of QFS and notice that each QFS write leads writes in multiple machines due to
data replication.     
% [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
% the cloud infrastructure services and are shared among many applications.]
%We see our hybrid deduplication scheme only occupies a small amount of system resources. 
%The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
%memory during duplicate detection.

Table ~\ref{tab:resource_usage} shows that  a single backup task per node can complete the backup of the entire
VM cluster in about 1.58 hours. Since there are about 25 VMs per machine, we could execute
more tasks in parallel at each machine. But adding more backup concurrency does not shorten the overall time
a lot because of the controlled  disk read time.
%,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
%at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.

{\bf Processing Time breakdown}.
Figure~\ref{fig:vc_srb_combined} shows
the  average  processing  time of  a VM segment under VC and SRB. 
VC uses $\sigma=2\%$ and $4\%$.
It has a breakdown of time for reading data, updating the metadata, network latency to visit
a remote machine, and index access for fingerprint comparison.
The change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time.
SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
it relies on this local machine to access its index (often on the disk, supported by a Bloom filter) 
and perform comparison.
VC is faster for index access because it conducts in-memory local search first and then
accesses  the PDS on distributed shared memory.  
SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
local meta data index.
Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.
%Figure~\ref{fig:vc_srb_combined} also reports the average backup time for a VM in VC when
%varying the PDS size.  It lists the time distribution for data reading,
%similarity-guided local search, cross-VM PDS lookup, and non-duplicate data writing. 
%While data reading dominates the backup process, PDS lookup spends about a similar amount
%of time as local search.

@@

@@

\begin{table*}[t]
    \centering
    \begin{tabular}{c|ccc|ccc}
    Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
    backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
    per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
    1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
    2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
    4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
    6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
    \end{tabular}
\caption{Throughput of software layers under different concurrency}
\label{tab:throughput}
\end{table*}
{\bf Throughput of software layers.}
Table~\ref{tab:throughput} shows the  average throughput of software layer
when I/O is throttled under 50MB/second and when there is no restriction.
%machine when all machine nodes execute one or multiple MV backup tasks.
``Raw'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the gap between this
column and  ``Raw" column is caused by significant data reduction by dirty bit and duplication
detection. Only non-duplicate chunks trigger a snapshot store write.
``QFS'' column is the write request traffic to the underlying file system after compression.
The underlying disk storage traffic will be three times or more because of replication.
The result shows that the backup service can deliver up to 5.46GB/second without I/O restriction
per machine with 6 concurrent backup tasks. With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine under 1.31 hours.

%To begin, on each node we write snapshots for 4 VMs concurrently, and gradually 
%increase number of VMs to 12 to saturate our system capability. 
%We observed 
%the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
%which is far beyond our QFS file system capability. The reason behind it is our efficient
%deduplication architecture and compression which greatly reduce the amount of data that needs to be written to
%the file system. The main bottleneck here is that our QFS installation only
%manages one disk per node, which prevents it from fully utilizing the the
%benefits of parallel disk access. We expect our architecture can
%perform even better in production clusters, which often have ten or more disks on each node.

@@

 \subsection{Effectiveness of Approximate Deletion}
 \begin{figure}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions}
     \label{fig:leakage}
 \end{figure}
